Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-17 paper/conclusion.tex
Fix typo in conclusion

A filter enforces invariant properties on data such that data that violate the invariant are not forwarded.
A monitor detects and alerts malicious behavior in the system. 
The actual behavior of such filters, monitors, and other high-assurance components are formally specified by code contracts.
A code contract is a dialect of the \agr\ language with formal semantics embedded in HOL for formal reasoning.
A code contract states assumptions on the inputs and then provides output guarantees that completely define the output in terms of the inputs and the current state of the component.
The code contract language itself is Turing complete.

Code contracts are validated with unit tests that are verified with the \agr\ verification engine.
A unit test in expressed in a test contract in the \agr\ language.
A test contract is a stylized contract that strengthens the input assumptions of a code contract to a single input and either weakens or leaves unchanged the code contract output guarantees.
\agr\ then proves whether or not the computation expressed in the code contract implements the test contract.
In this way, a designer is able to test the behavior of the code contract.
Once the code contract is tested, the \agr\ verification engine proves whether or note the system, with the added high-assurance components, meets its cyber requirements.

Code contracts are automatically synthesized to \ckml.
We discussed the \splt\ synthesis engine that iteratively transforms the code contract defined over streams of data into a state transitions function that only considers the current input and state of the component.
That state transition function is then rendered in \ckml, and the \ckml\ compiler compiles it to the target binary providing the proof of equivalence.

>>>>

A filter enforces invariant properties on data such that data that violate the invariant are not forwarded.
A monitor detects and alerts malicious behavior in the system. 
The actual behavior of such filters, monitors, and other high-assurance components are formally specified by code contracts.
A code contract is a dialect of the \agr\ language with formal semantics embedded in HOL4 for formal reasoning.
A code contract states assumptions on the inputs and then provides output guarantees that completely define the output in terms of the inputs and the current state of the component.
The code contract language itself is Turing complete.

Code contracts are validated with unit tests that are verified with the \agr\ verification engine.
A unit test in expressed in a test contract in the \agr\ language.
A test contract is a stylized contract that strengthens the input assumptions of a code contract to a single input and either weakens or leaves unchanged the code contract output guarantees.
\agr\ then proves whether or not the computation expressed in the code contract implements the test contract.
In this way, a designer is able to test the behavior of the code contract.
Once the code contract is tested, the \agr\ verification engine proves whether or not the system, with the added high-assurance components, meets its cyber requirements.

Code contracts are automatically synthesized to \ckml.
We discussed the \splt\ synthesis engine that iteratively transforms the code contract defined over streams of data into a state transition function that only considers the current input and state of the component.
That state transition function is then rendered in \ckml, and the \ckml\ compiler compiles it to the target binary providing the proof of equivalence.
